---
title: "625-HW3-Zejia"
author: "Zejia Liu"
date: "2022-11-22"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
```


Linear Regression Model:


1. Data set up:
```{r}
setwd("~/Desktop/Rstudio_work")
library(sas7bdat) 
library(dplyr)
mydata <- read.sas7bdat("completedata.sas7bdat")
head(mydata)

```
2. Model fitting:

Setting varibles:
```{r}
X_matrix <- cbind(1, mydata$Fatalism, mydata$Age, mydata$R_E)

Y_dep <- as.vector(mydata$Depression)

```

Setting models:
```{r}
fit_model <- function(aim_X, Y) {
    beta_hat <- solve(t(aim_X) %*% aim_X) %*% t(aim_X) %*% Y
    residuals <- Y - aim_X %*% beta_hat
    df <- nrow(aim_X) - ncol(aim_X)
    sigma_Sq <- (t(residuals) %*% residuals) / df
    Variance_beta <- as.vector(sigma_Sq) * (solve(t(aim_X) %*% aim_X))
    SE <- sqrt(diag(Variance_beta))

    # 95% Confidence Interval
    lower_bound <- beta_hat - 1.96 * SE
    upper_bound <- beta_hat + 1.96 * SE

    CI <- cbind(lower_bound, upper_bound)

    # Organize results into a nice dataframe that can be used to view results
    results_df <- data.frame(cbind(term = seq(length(beta_hat)),
                                   estimate = beta_hat,
                                   std_error = SE,
                                   conf_low = lower_bound,
                                   conf_high = upper_bound))

    colnames(results_df) <- c("Term", "Estimate", "Std. Error",
                              "95% CI Lower Bound", "95% CI Upper Bound")


    # Store the variables
    model_table <- list(parameters = as.vector(beta_hat),
                         residuals = residuals,
                         sigma_Sq = sigma_Sq, var_Mat = Variance_beta,
                         param_StdErrors = SE,
                         c_interval = CI,
                         results = results_df)

    return(model_table)

}
  
    
```


```{r}
OLS.fit <- fit_model(aim_X = X_matrix, Y = Y_dep)

OLS.fit

```

3. Checking Correctness: 

```{r}
lm.fit <- lm(formula = "Depression ~ Fatalism + Age + R_E", data = mydata)
all.equal(as.vector(lm.fit$coefficients), as.vector(OLS.fit$parameters))

```

```{r}
stdErr.lm <- summary(lm.fit)$coefficients[,"Std. Error"]
all.equal(as.vector(stdErr.lm), OLS.fit$param_StdErrors)
```

```{r}
all.equal(as.vector(OLS.fit$residuals), as.vector(lm.fit$residuals))
```
Based on the results above, we know that our implemented R function has the same beta esimates, standard error as the lm() function. Hence, we can comfirm our model's correctness.

4. Efficiency Analysis:

```{r}
library(microbenchmark)
microbenchmark::microbenchmark(
    lm(formula = "Depression ~ Fatalism + Age + R_E", data = mydata),
    fit_model(aim_X = X_matrix, Y = Y_dep)
)
```
We conclude that our optimized model runs faster than lm() function.
